\textls[-0]{\thetitle}

### 2023-04-02 introduction.tex
Adding List of Abbrev.
TODO

\item We contribute a prototypical implementation of our language
mechanism as a Coq plugin (\cref{sec:coqimpl}),
available at \url{https://anonymized-link-to-code}.
The plugin works by
compiling surface-language definitions into Coq modules parameterized by
explicit extensibility hooks.

>>>>

\item We contribute a prototypical implementation of our language
mechanism as a Coq plugin (\cref{sec:coqimpl}),
available at \url{https://anonymized-link-to-code}.\YZ{TODO}
The plugin works by
compiling surface-language definitions into Coq modules parameterized by
explicit extensibility hooks.
